The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-22 src/ms.tex
adjust wording about leap seconds

\paragraph{Time}
In astronomy, time accuracy down to the (nano)second is frequently important.
Whether for planning observations or crunching pulsar or VLBI data, missing
seconds meaningfully impact results. In past versions of \astropypkg, when using
\astropyTime, leap seconds had to be manually applied; now, leap
seconds are applied automatically. Moreover, \astropypkg updates internal time
data files to ensure that the correct leap second adjustment is always used. For
reproducibility with older code, \astropyLeapSeconds\ may also be
manually applied.

>>>>

\paragraph{Time}
In astronomy, time accuracy down to the (nano)second is frequently important.
Whether for planning observations or crunching pulsar or VLBI data, missing
seconds meaningfully impact results. In past versions of \astropypkg, when using
\astropyTime, leap second tables had to be manually updated. Now, \astropypkg
automatically updates internal time data files to ensure that the correct leap
second adjustment is always used. For reproducibility with older code,
\astropyLeapSeconds\ may also be manually applied.
